Plume-SPH 1.0: A 3D dust-gas volcano plume model based on smoothed particle hydrodynamics

### 2016-10-03 Manuscripts_GMD.tex
add subsections in introduction

@@

@@

@@

@@

Simulation of volcano plume with acceptable accuracy requires fine resolutions (very high particle counts) that cannot be accomplished without parallel computing within given time window. The core solver of our model is parallelized by MPI (message passing interface standard) parallelism. In addition, a dynamic load balancing strategy is also adopted. What's more, imposing of some types of boundary conditions (such as eruption boundary condition) requires dynamically adding and removing of particles during simulation. To address this issue, we adopt an efficient data management scheme based on SFC (space filling curve) and hash table.\\

@@

Where $CFL_p$ is a safety coefficient which has similar function as the normal $CFL$ number. Too small $CFL_p$ will slow down simulation while too large $CFL_p$ will lose its ability of mitigate numerical fluctuation near the boundary. The proper $CFL_p$ is determined by series of simulation tests. 

@@

As for domain decomposition, even though more complicated graph-based partitioning tools \citep {biswas1999experiments} might get higher quality decomposition, they requires much more effort in programming and computation. So we adopt an easy-programming scheme based on SFC \citep {patra1999efficient}.\\

>>>>

\subsection{Volcanic ash hazards}

@@

\subsection{Existing plume models}

@@

\subsection{Features of SPH}

@@

\subsection{Our contribution}

@@

Simulation of volcano plume with acceptable accuracy requires fine resolutions (very high particle counts) that cannot be accomplished without parallel computing within given time window. The core solver of our model is parallelized by MPI (message passing interface standard) parallelism. In addition, a dynamic load balancing strategy is also developed. What's more, imposing of some types of boundary conditions (such as eruption boundary condition) requires dynamically adding and removing of particles during simulation. To address this issue, we adopt an efficient data management scheme based on time dependent SFC (space filling curve) and hash table. The computational cost is further reduced by adjusting simulation domain adaptively.\\

@@

Where $CFL_p$ is a safety coefficient which has similar function as the normal $CFL$ number. Too small $CFL_p$ will slow down simulation while too large $CFL_p$ will lose its ability of mitigate numerical fluctuation near the boundary. The proper $CFL_p$ is determined by series of simulation tests. \\
In subfigure b of Fig. \ref{fig:bc_and_domain_decomp}, different type of boundary conditons are marked with different color. The red portion are main computational domain. 

@@

As for domain decomposition, even though more complicated graph-based partitioning tools \citep {biswas1999experiments} might get higher quality decomposition, they requires much more effort in programming and computation. So we adopt an easy-programming scheme based on SFC \citep {patra1999efficient}. Subfigure c of Fig. \ref{fig:bc_and_domain_decomp} shows a cross section view of domian decomposition.\\
